Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-19 paper_knowledge.tex
Give more freedom to Latex to place figures
Minor revisions by Raquel

Communcation between these components is build as streams of symbolic facts,
where knowledge that the robot manipulate is made explicit.
This leads us to the idea of a \emph{knowledge-oriented architecture} which is
discussed at the end of the article.

@@

\begin{figure}[!t] \centering
\includegraphics[width=\columnwidth]{images/looks.jpg} \caption{Representation
of the field of view (FOV) and the field of attention (FOA) of the human.}
\label{fig::vis} \end{figure}

@@

\begin{figure}[!t] 
	\centering
	\includegraphics[width=0.8\columnwidth]{images/reach.jpg} 
	\caption{Different reaching postures for the human: the bottle and the 
	box are reachable, while the teddy bear is not.} 
	\label{fig::reach} 
\end{figure}

@@

\begin{figure}[!ht]
\centering
  \includegraphics[width=0.9\linewidth]{images/dialog_module_simple.png}
  \caption{The {\sc Dialogs} module has three main steps: the parsing,
  the interpretation and the verbalization. The interpretation module is
  responsible for both the \emph{resolution} and the semantic content
  \emph{analysis and translation}.} 
  \label{fig|dialog}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\scriptsize
\begin{alltt}
>> IMPERATIVE
VP: \textbf{remember} (present simple)
    SUBSENTENCE (aim: that)
      NP: \textbf{I}
      VP: \textbf{want} (present simple)
        direct objects: 
          NP: \textbf{you}
        secondary VP: \textbf{give} ()
              direct objects:
                NP: my \emph{nice blue} \textbf{bottle}
              indirect objects:
                NP: \textbf{me}
\end{alltt}
\end{center}
\caption{Raw output of the {\sc Dialogs} parser after processing the
sentence: ``remember that I want you to give me my nice blue bottle.'' 
Nominal groups are not grounded yet.} 
\label{dialog|parser_output}
\end{figure}

@@

Figure~\ref{dialog|ex1} shows a first example of human discourse grounding and
the extraction of informational content. We assume that the robot knowledge
base only contains two initial statements in the human model. The user
asserts a new one: ``The yellow banana is big!''. 
We first want to match the nominal group \emph{The yellow banana} to an already
known concept (algorithm~\ref{algo|Resolution}), and second to translate the property \emph{is big} into a predicate (\emph{hasSize}) to state its semantics.

@@

The robot selects an unknown object from the table, shows it to the user, and
asks about its name and type (Figure~\ref{fig|kimpwatching}). The user
interacts with the robot through a dedicated bridge, allowing him/her to chat with
the robot with a standard Jabber instant messaging client.
Figure~\ref{tab|transcript_kimp} shows a chat session with Rosie performing the
naming experiment. The human describes the object until the robot recognizes a
type it already knows. More precisely, the robot recursively asks the human for the categories the object belongs to until reaching a known one. At this point, the robot is able to connect the new object information to already known concepts. Therefore, the robot
accurately anchors perception in its symbolic model and it is able to reason
about it.  The learning process starts over again with each unknown object. To
further exploit the knowledge reasoner in this experiment, we ask the robot
which object do not belong to a typical breakfast table, \ie we ask for the odd
objects. In this case, it corresponds to objects that are neither of type
\concept{Tableware} nor \concept{Food}.

@@

\begin{figure}[!ht]
\centering
	\begin{tabular}{r|p{7cm}}
	\chatN{rosie} & Servus! The Bavarian robot is up and fit! \\
	\chatN{rosie} & What is the name of the white cluster on the table? \\
	\chatN{human} & ``Rosie's mug'' \\
	\chatN{rosie} &\emph{[\stmt{obj\_01 label "Rosie's mug"} added]}\\
				& What kind of object is ``Rosie's mug''? \\
	\chatN{human} & Mug \\
	\chatN{rosie} & \emph{[\stmt{obj\_01 type Mug} added]}\\
			& What is a Mug?\\ 
	\chatN{human} & Tableware\\
	\chatN{rosie} & \emph{[\stmt{Mug subClassOf Tableware} added. Rosie already
	knows about \emph{Tableware} (it belongs to the common-sense ontology), so
	the description of this object ends.]}\\
	& (...) \\
	\chatN{rosie} &  What is the name of the black cluster on the table? \\
	\chatN{human} & ``my\_laptop'' \\
	\chatN{rosie} & What kind of object is ``my\_laptop''? \\
	\chatN{human} & Computer \\
	\chatN{rosie} & What is a Computer? \\
	\chatN{human} & Artifact \\
	\chatN{rosie} & Do you want me to learn more objects? \\
	\chatN{human} & no \\
	\chatN{rosie} & These objects are odd: ``my\_laptop'' \\
	\end{tabular}
	\caption{Transcript of a Jabber session with the robot Rosie.}
	\label{tab|transcript_kimp}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{scriptsize}
\begin{tikzpicture} %[level/.style={sibling distance=30mm/#1},scale=0.8]
	%[edge from parent fork down,
	%every node/.style={fill=black!30,rounded corners},
	%[parent anchor=east,child anchor=west,grow=east,
	%edge from parent/.style={thick,draw}]
	\node {Artifact}
	child {node {Tableware}
		child {node {Bottle}}
		child {node {Cup}}
		}
	child {node {GameObject}}
	child {node {Furniture}
			child {node {Table}}
			child {node {Chair}}
			child {node {Shelf}}};
\end{tikzpicture}
\end{scriptsize}
\caption{Example of object categorization used in the scenario.}
\label{fig|objectsSpyGame}			
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfigure[]
  {\includegraphics[width=0.95\linewidth]{images/situationAssessment1.png}\label{a}}
  \subfigure[]
  {\includegraphics[width=0.95\linewidth]{images/situationAssessment2.png}\label{b}}
	\caption{Situation assessment during initialization: a) before placing the
	objects on the table, and b) after placing them. In each image the snapshots
	correspond to: real environment (top-left sub-image); processed image to
	identify the tagged objects (bottom-left sub-image); and the 3D environment
	(right sub-image).}
	\label{fig|sitAssessRoman}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \subfigure[]
  {\includegraphics[width=0.9\linewidth]{images/inTheBox1.jpg}\label{a}}
  \subfigure[]
  {\includegraphics[width=0.9\linewidth]{images/inTheBox2.jpg}\label{b}}
\caption{(a) Jerry asks Jido for the content of the box and (b) points at it.}
  \label{fig|pointing}
\end{figure}

@@

This architecture moves away from standard layered approaches: Interactions
between components are mostly bidirectional and we do not have a concept of
layers of abstraction (we do, however, have access to the robot lower levels
to execute actions, but all cognition-related modules live at the same level).
This is especially visible for the dialogue input processing: this component
does not simply act as an alternative perceptual input to the symbolic
database, but also actively queries previously acquired knowledge to
disambiguate and validate the newly created symbolic knowledge.

@@

We hope as well that our contribution may contribute to fill the gap between
robotics and psychology. Our architecture provides easier-to-reach entry points
to implement some classical psychology tests to robots. We presented
experiments focused on issues related to perspective taking. By explicitly
enabling independent modeling of the beliefs of each agent, our architecture is
especially well suited to set up cognitive and psychological experiments (such
as the \emph{False-Belief} experiment~\cite{Leslie2000}), which we plan to
further explore.

>>>>

Communcation between these components is build as streams of symbolic facts,
where knowledge manipulated by the robot is made explicit.
This leads us to the idea of a \emph{knowledge-oriented architecture}, which is
discussed at the end of the article.

@@

\begin{figure}%[!t] 
\centering
\includegraphics[width=\columnwidth]{images/looks.jpg} \caption{Representation
of the field of view (FOV) and the field of attention (FOA) of the human.}
\label{fig::vis} \end{figure}

@@

\begin{figure}%[!t] 
	\centering
	\includegraphics[width=0.8\columnwidth]{images/reach.jpg} 
	\caption{Different reaching postures for the human: the bottle and the 
	box are reachable, while the teddy bear is not.} 
	\label{fig::reach} 
\end{figure}

@@

\begin{figure}%[!ht]
\centering
  \includegraphics[width=0.9\linewidth]{images/dialog_module_simple.png}
  \caption{The {\sc Dialogs} module has three main steps: the parsing,
  the interpretation and the verbalization. The interpretation module is
  responsible for both the \emph{resolution} and the semantic content
  \emph{analysis and translation}.} 
  \label{fig|dialog}
\end{figure}

@@

\begin{figure}%[!ht]
\begin{center}
\scriptsize
\begin{alltt}
>> IMPERATIVE
VP: \textbf{remember} (present simple)
    SUBSENTENCE (aim: that)
      NP: \textbf{I}
      VP: \textbf{want} (present simple)
        direct objects: 
          NP: \textbf{you}
        secondary VP: \textbf{give} ()
              direct objects:
                NP: my \emph{nice blue} \textbf{bottle}
              indirect objects:
                NP: \textbf{me}
\end{alltt}
\end{center}
\caption{Raw output of the {\sc Dialogs} parser after processing the
sentence: ``remember that I want you to give me my nice blue bottle.'' 
Nominal groups are not grounded yet.} 
\label{dialog|parser_output}
\end{figure}

@@

Figure~\ref{dialog|ex1} shows a first example of human discourse grounding and
the extraction of informational content. We assume that the robot knowledge
base only contains two initial statements in the human model. The user
asserts a new one: ``The yellow banana is big!''. 
We first want to match the nominal group \emph{The yellow banana} to an already
known concept (algorithm~\ref{algo|Resolution}), and second to translate the property \emph{is big} into a predicate ({\tt hasSize}) to state its semantics.

@@

The robot selects an unknown object from the table, shows it to the user, and
asks about its name and type (Figure~\ref{fig|kimpwatching}). The user
interacts with the robot through a dedicated bridge, allowing him/her to chat with
the robot with a standard Jabber instant messaging client.
Figure~\ref{tab|transcript_kimp} shows a chat session with Rosie performing the
naming experiment. The human describes the object until the robot recognizes a
type it already knows. More precisely, the robot recursively asks the human for the categories the object belongs to until reaching a known one. At this point, the robot is able to connect the new object information to already known concepts. Therefore, the robot
accurately anchors perception in its symbolic model and it is able to reason
about it.  The learning process starts over again with each unknown object. To
further exploit the knowledge reasoner in this experiment, we ask the robot
which object does not belong to a typical breakfast table, \ie we ask for the odd
objects. In this case, it corresponds to objects that are neither of type
\concept{Tableware} nor \concept{Food}.

@@

\begin{figure}%[!ht]
\centering
	\begin{tabular}{r|p{7cm}}
	\chatN{rosie} & Servus! The Bavarian robot is up and fit! \\
	\chatN{rosie} & What is the name of the white cluster on the table? \\
	\chatN{human} & ``Rosie's mug'' \\
	\chatN{rosie} &\emph{[\stmt{obj\_01 label "Rosie's mug"} added]}\\
				& What kind of object is ``Rosie's mug''? \\
	\chatN{human} & Mug \\
	\chatN{rosie} & \emph{[\stmt{obj\_01 type Mug} added]}\\
			& What is a Mug?\\ 
	\chatN{human} & Tableware\\
	\chatN{rosie} & \emph{[\stmt{Mug subClassOf Tableware} added. Rosie already
	knows about \emph{Tableware} (it belongs to the common-sense ontology), so
	the description of this object ends.]}\\
	& (...) \\
	\chatN{rosie} &  What is the name of the black cluster on the table? \\
	\chatN{human} & ``my\_laptop'' \\
	\chatN{rosie} & What kind of object is ``my\_laptop''? \\
	\chatN{human} & Computer \\
	\chatN{rosie} & What is a Computer? \\
	\chatN{human} & Artifact \\
	\chatN{rosie} & Do you want me to learn more objects? \\
	\chatN{human} & no \\
	\chatN{rosie} & These objects are odd: ``my\_laptop'' \\
	\end{tabular}
	\caption{Transcript of a Jabber session with the robot Rosie.}
	\label{tab|transcript_kimp}
\end{figure}

@@

\begin{figure}%[!ht]
\centering
\begin{scriptsize}
\begin{tikzpicture} %[level/.style={sibling distance=30mm/#1},scale=0.8]
	%[edge from parent fork down,
	%every node/.style={fill=black!30,rounded corners},
	%[parent anchor=east,child anchor=west,grow=east,
	%edge from parent/.style={thick,draw}]
	\node {Artifact}
	child {node {Tableware}
		child {node {Bottle}}
		child {node {Cup}}
		}
	child {node {GameObject}}
	child {node {Furniture}
			child {node {Table}}
			child {node {Chair}}
			child {node {Shelf}}};
\end{tikzpicture}
\end{scriptsize}
\caption{Example of object categorization used in the scenario.}
\label{fig|objectsSpyGame}			
\end{figure}

@@

\begin{figure}%[!t]
\centering
  \subfigure[]
  {\includegraphics[width=0.95\linewidth]{images/situationAssessment1.png}\label{a}}
  \subfigure[]
  {\includegraphics[width=0.95\linewidth]{images/situationAssessment2.png}\label{b}}
	\caption{Situation assessment during initialization: a) before placing the
	objects on the table, and b) after placing them. In each image the snapshots
	correspond to: real environment (top-left sub-image); processed image to
	identify the tagged objects (bottom-left sub-image); and the 3D environment
	(right sub-image).}
	\label{fig|sitAssessRoman}
\end{figure}

@@

\begin{figure}%[!ht]
  \centering
  \subfigure[]
  {\includegraphics[width=0.9\linewidth]{images/inTheBox1.jpg}\label{a}}
  \subfigure[]
  {\includegraphics[width=0.9\linewidth]{images/inTheBox2.jpg}\label{b}}
\caption{(a) Jerry asks Jido for the content of the box and (b) points at it.}
  \label{fig|pointing}
\end{figure}

@@

This architecture moves away from standard layered approaches. Interactions
between components are mostly bidirectional and we do not have a concept of
layers of abstraction (we do, however, have access to the robot lower level
modules to execute actions, but all cognition-related modules live at the same
level). This is especially visible for the dialogue input processing. This
component does not simply act as an alternative perceptual input to the
symbolic database, but also actively queries previously acquired knowledge to
disambiguate and validate the newly created symbolic knowledge.

@@

We hope as well that our contribution may contribute to fill the gap between
robotics and psychology. Our architecture provides easier-to-reach entry points
to implement some classical psychology tests to robots. We presented
experiments focused on issues related to perspective taking. By explicitly
enabling independent modeling of the beliefs of each agent, our architecture is
especially well suited to set up cognitive and psychological experiments (such
as the \emph{False-Belief} experiment), which we plan to
further explore.
